Kinematics of the Palomar 5 stellar stream from RR Lyrae stars

### 2019-09-30 paper/main.tex

\begin{figure*}[t]
\begin{center}
\includegraphics[width=\textwidth]{members.pdf}
\caption{Sky positions of RRLs with Pal 5 colored by membership probability, \changes{but stars with probability $<0.1$ are plotted with a smaller marker.}
The background greyscale shows the surface density of CMD-filtered main sequence stars from \citet{Bonaca:2019}.
Note that the membership probability does not incorporate sky position information, but a clear over-density of high-probability RRL members do trace the stream on the sky.
Purple lines outline the stream track window defined in \citet{Bonaca:2019} and used here to exclude stream stars when constructing the background model.}
\label{fig:members}
\end{center}
\end{figure*}

>>>>

\begin{figure*}[t]
\begin{center}
\includegraphics[width=\textwidth]{members.pdf}
\caption{Sky positions of RRLs with Pal 5 colored by membership probability, \changes{but stars with probability $<0.1$ are plotted with a smaller marker.}
The background greyscale shows the surface density of CMD-filtered main sequence stars from \citet{Bonaca:2019}.
Note that the membership probability does not incorporate sky position information, but a clear over-density of high-probability RRL members do trace the stream on the sky.
Purple lines outline the stream track window defined in \citet{Bonaca:2019} and used here to exclude stream stars when constructing the background model.
The inset panel shows a $1.5^\circ$ by $1.5^\circ$ zoom-in around the Pal 5 cluster, with the Jacobi radius of the cluster shown as a large red circle.
}
\label{fig:members}
\end{center}
\end{figure*}
